Modal type theory based on the intuitionistic epistemic logic

### 2018-01-20 article.tex
added subject reduction
small fixes

  6) $M \rightarrow_{\beta} N \Rightarrow {\bf pure \: M} \rightarrow_{\beta} {\bf pure \: N}$

  7) $\lambda x. f x \rightarrow_{\eta} f$;

  8) $\langle \pi_1 P, \pi_2 P \rangle \rightarrow_{\eta} P$;

  9) ${\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N \rightarrow_{\eta} {\bf pure \:} N$;

  10) ${\bf let \: pure \:} x = M {\: \bf in \: } x \rightarrow_{\eta} M$;

  11) $M \rightarrow_{\eta} N \Rightarrow {\bf pure \: M} \rightarrow_{\eta} {\bf pure \: N}$
  \end{defin}

@@

\begin{theorem} Subject reduction
\end{theorem}

@@

  Let $\langle \mathcal{C}, \oplus_1, \mathds{1} \rangle$ and $\langle \mathcal{D}, \oplus_2, \mathds{1}' \rangle$ are monoidal categories.

  A lax monoidal functor $\mathcal{F} : \langle \mathcal{C}, \oplus_1, \mathds{1} \rangle \to \langle \mathcal{D}, \oplus_2, \mathds{1}' \rangle$ is a functor
  $\mathcal{F} : \mathcal{C} \to \mathcal{D}$ with additional natural transformations:

>>>>

  6) $\lambda x. f x \rightarrow_{\eta} f$;

  7) $\langle \pi_1 P, \pi_2 P \rangle \rightarrow_{\eta} P$;

  8) ${\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N \rightarrow_{\eta} {\bf pure \:} N$;

  9) ${\bf let \: pure \:} x = M {\: \bf in \: } x \rightarrow_{\eta} M$;

  10) $M \rightarrow_{\beta \eta} N \Rightarrow {\bf pure \: M} \rightarrow_{\beta \eta} {\bf pure \: N}$
  \end{defin}

@@

\begin{theorem} Subject reduction

  Let $\Gamma \vdash M : A$ and $M \twoheadrightarrow_{\beta \eta} N$, then $\Gamma \vdash N : A$

\end{theorem}

For cases with application, abstraction and pairs see \cite{Morten} \cite{Pierce}.

1)
  Let $\Gamma \vdash {\bf let \: pure \:} \langle \vec{x}, y, \vec{z} \rangle = \langle \vec{M}, {\bf let \: pure \: } \vec{w} = \vec{N} {\bf \: in \: } Q, \vec{P} \rangle {\: in \:} R : {\bf K}B$,
  then $\Gamma {\bf let \: pure \:} \langle \vec{x}, \vec{w}, \vec{z} \rangle = \langle \vec{M}, \vec{N}, \vec{P} \rangle \: { \bf in } \: R [y := Q] : {\bf K}B$

2) Let $\Gamma \vdash {\bf let \: pure \:} x = M {\: \bf in \: } x : {\bf K}A$, then $\Gamma \vdash M : {\bf K}A$.

See \cite{ModalK}.

3) Let $\Gamma \vdash {\bf let \: pure \:} \vec{x} = {\bf pure \:} \vec{M} {\: \bf in \:} N : {\bf K}B$.

By generation $\Gamma \vdash {\bf pure \:} \vec{M} : {\bf K}\vec{A}$ and $\vec{x} : \vec{A} \vdash N : B$.
\\ Moreover, $\Gamma \vdash \vec{M} : \vec{A}$. By weakening and substitution lemma $\Gamma \vdash N [\vec{x} = \vec{M}] : B$.
\\ By ${\bf K}_I$, $\Gamma \vdash {\bf pure \:} N [\vec{x} := \vec{M}] : {\bf K}B$.

4) Let $\vdash {\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N : {\bf K}A$

By generation $\vdash N : A$. \\ So $\vdash {\bf pure \:} N : {\bf K}A$ by ${\bf K}_I$.

5) Let $\Gamma \vdash {\bf pure \:} M : A$ and $M \twoheadrightarrow_{\beta \eta} N$.

By generation $\Gamma \vdash M : A$ and $\Gamma \vdash N : A$ by assumption.
\\ So $\Gamma \vdash {\bf pure \:} N : {\bf K}A$.

@@

  Let $\langle \mathcal{C}, \otimes_1, \mathds{1} \rangle$ and $\langle \mathcal{D}, \otimes_2, \mathds{1}' \rangle$ are monoidal categories.

  A lax monoidal functor $\mathcal{F} : \langle \mathcal{C}, \otimes_1, \mathds{1} \rangle \to \langle \mathcal{D}, \otimes_2, \mathds{1}' \rangle$ is a functor
  $\mathcal{F} : \mathcal{C} \to \mathcal{D}$ with additional natural transformations:
